Effort and Delay Discounting in a Foraging Environment

### 2019-04-24 Cost2/Cost2_prereg.Rmd
adjusting spacing of code

``` {r Basic Prepping, echo=FALSE}  
# params for reference
handling <- c(2,10,14)
cond <- c("Wait","Cognitive","Physical","Easy")

@@

colnames(summaryData) <- c("Group","propComplete","Earnings","RT","forcedTravel")

>>>>

``` {r Basic Prepping, echo=FALSE}  
# params for reference
handling <- c(2, 10, 14)
cond <- c("Wait", "Cognitive", "Physical", "Easy")

@@

colnames(summaryData) <- c("Group", "propComplete", "Earnings", "RT", "forcedTravel")
